% TEX root = ../CV.tex
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%-------------------------------------------------------------------------------
\cventry
{$\;$}
{2021}
{$\;$}
{$\;$}
{
  \begin{cvitems} % Description(s)
      \item {
        \begin{flushleft}
          Morrison, M. J., \textbf{Razo-Mejia, M.}, \& Phillips, R. (2021).
          \textit{Reconciling Kinetic and Equilibrium Models of Bacterial
          Transcription}. PLoS comp. bio. \texttt{
          \href{https://github.com/RPGroup-PBoC/bursty_transcription}{GitHub repository}
          }
          \linebreak
          https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1008572
        \end{flushleft}
      }
  \end{cvitems}
}
%-------------------------------------------------------------------------------
  \cventry
    {$\;$}
    {2020}
    {$\;$}
    {$\;$}
    {
      \begin{cvitems} % Description(s)
          \item {
            \begin{flushleft}
              \textbf{Razo-Mejia, M.}, et al. (2020).
              \textit{First-principles prediction of the information processing
              capacity of a simple genetic circuit}. Phys. Rev. E 022404, 1–14.
              \texttt{
              \href{https://www.rpgroup.caltech.edu/chann_cap/}{Paper website} 
              }
              and
              \texttt{
              \href{https://github.com/RPGroup-PBoC/chann_cap}{GitHub repository}
              }
              \linebreak
              http://doi.org/10.1103/PhysRevE.102.022404
            \end{flushleft}
          }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {$\;$}
    {2019}
    {$\;$}
    {$\;$}
    {
      \begin{cvitems} % Description(s)
        \item {
        \begin{flushleft}
          Chure, G., \textbf{Razo-Mejia, M.}, Belliveau, N. M., Einav, T.,
          Kaczmarek, Z. A., Barnes, S. L., Lewis, M., Phillips, R. (2019).
          \textit{Predictive shifts in free energy couple mutations to their
          phenotypic consequences}. PNAS, 201907869.
          \texttt{
          \href{https://www.rpgroup.caltech.edu/mwc_mutants/}{Paper website} 
          }
          and
          \texttt{
          \href{https://github.com/RPGroup-PBoC/mwc_mutants}{GitHub repository}
          }
          \linebreak
          https://doi.org/10.1073/pnas.1907869116
        \end{flushleft}
        }
        \item {
          \begin{flushleft}
            Foster, P. J., \textbf{Razo-Mejia, M.}, Phillips, R. (2019).
            \textit{Measuring the Energetic Costs of Embryonic Development}.
            Developmental Cell, 48(5), 591?592.\linebreak
            http://doi.org/10.1016/j.devcel.2019.02.016
          \end{flushleft}
        }
        \item {
          \begin{flushleft}
            Phillips, R., Belliveau, N. M., Chure, G., Garcia, H. G.,
            \textbf{Razo-Mejia, M.}, Scholes, C. (2019). \textit{Figure 1
            Theory Meets Figure 2 Experiments in the Study of Gene Expression}.
            Annual Review of Biophysics, 48(1), 121?163.\linebreak
            http://doi.org/10.1146/annurev-biophys-052118-115525
          \end{flushleft}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {$\;$}
    {2018}
    {$\;$}
    {$\;$}
    {
      \begin{cvitems}
        \item {
        \begin{flushleft}
          \textbf{Razo-Mejia, M.}*, Barnes, S. L.*, Belliveau, N. M.*, Chure,
          G.,* Einav, T.*, Lewis, M., Phillips, R. (2018). \textit{Tuning
          Transcriptional Regulation through Signaling : A Predictive Theory of
          Allosteric Induction}. Cell Systems, 1-14. * These authors contribute
          equally. 
          \texttt{
            \href{http://www.rpgroup.caltech.edu/mwc_induction/}{Paper website} 
            }
            and
            \texttt{
            \href{http://www.github.com/rpgroup-pboc/mwc_induction}{GitHub repository}
            }
          \linebreak
          http://doi.org/10.1016/j.cels.2018.02.004.
        \end{flushleft}
        }
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {$\;$}
    {2015}
    {$\;$}
    {$\;$}
    {
      \begin{cvitems}
        \item {
        \begin{flushleft}
           Zelcbuch, L., \textbf{Razo-Mejia, M.}, Herz, E., Yahav S.,
           Antonovsky N., Kroytoro H., Milo R., Bar-Even A. (2015). \textit{An
           in vivo metabolic approach for deciphering the product specificity
           of glycerate kinase proves that both E. coli's glycerate kinases
           generate 2-phosphoglycerate}. Plos One, 10(3), e0122957.\linebreak
           http://doi.org/10.1371/journal.pone.0122957
        \end{flushleft}
        }
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
    {$\;$}
    {2014}
    {$\;$}
    {$\;$}
    {
      \begin{cvitems}
        \item {
        \begin{flushleft}
           \textbf{Razo-Mejia, M.}, Boedicker, J. Q., Jones, D., DeLuna, a,
           Kinney, J. B., \& Phillips, R. (2014). \textit{Comparison of the
           theoretical and real-world evolutionary potential of a genetic
           circuit}. Physical Biology, 11(2), 026005.\linebreak
           http://doi:10.1088/1478-3975/11/2/026005
        \end{flushleft}
        }
      \end{cvitems}
    }

% \cventry
%     {$\;$}
%     {year}
%     {$\;$}
%     {$\;$}
%     {
%       \begin{cvitems}
%         \item {
%         \begin{flushleft}
%            Citation goes here
%         \end{flushleft}
%         }
%       \end{cvitems}
%     }

\end{cventries}
